CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-11-27 paper.Rmd
Split lines to avoid bleeding into margin. Addresses #7.

```{r, eval=FALSE}
# (3) Run the PFUDatabase pipeline to create RUVY matrices.
targets::tar_make_future(script = file.path("ExampleFolder", "_targets_pfudatabase.R"), 
                         workers = 4)
# (4) Run the PFUAggDatabase pipeline to aggregate 
#     energy and calculate efficiencies.
targets::tar_make_future(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
                         workers = 4)
```

>>>>

```{r, eval=FALSE}
# (3) Run the PFUDatabase pipeline to create RUVY matrices.
targets::tar_make_future(
  script = file.path("ExampleFolder", "_targets_pfudatabase.R"), 
  workers = 4
)
# (4) Run the PFUAggDatabase pipeline to aggregate 
#     energy and calculate efficiencies.
targets::tar_make_future(
  script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
  workers = 4
)
```
